---
title: "Advancing Programming with R trial run"
subtitle: "QMD modified by Aashvi Shah - June 2024"
author: |
  Aashvi Shah 23200323
date: " 12th June 2024, 10:14 am"
format:
  beamer:
    template: header_beamer.tex
    toc: false
fontsize: 11pt
execute: 
  eval: true
  echo: true
  message: false
  warning: false
  size: 11
output:
  beamer_presentation:
    fig_height: 4  # Adjusted height
    fig_width: 6   # Adjusted width
---

```{r}
knitr::opts_chunk$set(
  echo = TRUE,           # Show code by default
  message = FALSE,       # Suppress messages
  warning = FALSE,       # Suppress warnings
  fig.width = 4,         # Default figure width
  fig.height = 3,        # Default figure height
  fig.align = 'center',  # Center-align figures
  size = 'footnotesize'  # Use a smaller font size for code and output
)

```

```{r}
library(ggplot2)
library(png)
file_path <- "/Users/aashvishitalshah/Downloads/iris-machinelearning.png"
image_data <- readPNG(file_path)
plot(1:2, type = "n", xlab = "", ylab = "", xlim = c(0, 1), ylim = c(0, 1))
rasterImage(image_data, 0, 0, 1, 1)
```

# **Exploring the Relationship Between Sepal Length and Width in Iris Flowers**

## Introduction

The *"iris"* dataset contains measurements of sepal and petal dimensions for three species of iris flowers: ***setosa, versicolor, and virginica***. In this analysis, we'll focus on the relationship between sepal length and sepal width across these different species.

## **Descriptive Statistics**

**Before plotting the data, let's start by examining some descriptive statistics of the sepal length**

**and width variables.**

```{r}
#| echo: false
# Load dataset
data(iris)

# Summary statistics
summary(iris$Sepal.Length)
summary(iris$Sepal.Width)

```

### **Sepal Length**

**1) Minimum**: 4.3

**2) Maximum**: 7.9

**3) Mean**: 5.84

**4) Median**: 5.8

**5) Standard Deviation**: 0.83

### **Sepal Width**

**1) Minimum**: 2.0

**2) Maximum**: 4.4

**3) Mean**: 3.06

**4) Median**: 3.0

**5) Standard Deviation**: 0.44

## **Plotting the Relationship**

Now, let's visualize the relationship between sepal length and width using a scatter plot,

with different colors representing each species of iris flower.

```{r}
# Plotting the relationship between sepal length and width
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_point() +
  labs(title = "Relationship Between Sepal Length and Width",
       x = "Sepal Length",
       y = "Sepal Width") +
  theme_minimal()

```

## **Interpretation**

The scatter plot above illustrates the relationship between sepal length and sepal width for iris flowers of different species.

From the plot, we observe variations in sepal dimensions across the three species: setosa, versicolor, and virginica. Generally, there appears to be a positive relationship between sepal length and width, with some variations within each species.

This insight could provide valuable information for distinguishing between different species of iris flowers based on their sepal characteristics.
